An Ethnography of Online Performance Artists

### 2017-03-17 proposals/Brown_Magic_Grant_2017/main.tex
spent a while working on the abstract

\AtBeginBibliography{\small}
\thispagestyle{empty}

@@

\def\maketitle{%
\par{\centering {\scshape \LARGE \textbf{\@title}}%
\par{\@author}
\par{DRAFT \DTMcurrenttime~\today}%
\par}}
% \smallskip \hrule \smallskip }

\definecolor{PineGreen}{HTML}{008800}
\definecolor{Red}{HTML}{FF0000}
\definecolor{Blue}{HTML}{0000FF}
\definecolor{Black}{HTML}{000000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{Red}[al2: #1]}}

\title{An Ethnography of Online Performance Artists}
\author{Ali Alkhatib \& Jeffrey Nagy}
\date{\today}
\urlstyle{same}
\hypersetup{
  colorlinks,
  citecolor=Black,
  urlcolor=Blue}

\definecolor{Blue}{HTML}{0000FF}
\newcommand{\topic}[1]{{\color{Blue}#1}}
\renewcommand{\topic}[1]{{#1}}
\definecolor{Gray}{HTML}{A0A0A0}
\newcommand{\ugh}[1]{{\color{Gray}#1}}
\newenvironment{blah}{\par\color{Gray}\itshape}{\par}

\begin{document}
  \maketitle
  \begin{abstract}
  Online video sharing and streaming platforms have grown quickly in the past decade
  to support an emerging community of unconventional entertainers.
  This eclectic group of artists has collectively been
  exploring boundaries and experimenting with styles and expectations,
  critically influencing both our cultural expectations of performers and the norms of performance itself.
  But these dramatic shifts have coincided with turmoil among this new class of entertainers and artists.
  The frustration and turmoil they're experiencing
  --- both with one another and with the very platform on which they ``work'' ---
  calls for a better understanding of the culture and position of this nascent culture.
  We propose to conduct ethnographic fieldwork in this domain,
  initially informed by a historical framing, but
  ultimately studying how digitally mediated publics such as these affect
  the politics of this group of performers.
  \end{abstract}

% \section*{Situation}
\topic{Online video sharing % \ali{, such as YouTube and Vimeo,}
and streaming sites % \ali{, like Twitch and others,}
have garnered the attention of audiences around the world
in the span of little more than a decade.} % taken on characteristics of
So widely used are these platforms
that it would be fair to call them ``publics'' in the Deweyan sense~\cite{dewey2012public,disalvo2009design};
content producers
--- ``YouTubers'' and ``streamers'' ---
have begun to make their livings on these sites.
Indeed, these performers have come to rely on
the technical infrastructure these platforms provide as well as
the access to audiences that these platforms provide as well.
In doing so, these sites have in a real sense democratized media and entertainment industries by
making the avenues to large audiences substantially more accessible.
And thus, in these transformations into publics, what started as
a recreational hobby
has become a bustling hub for professional artists to
engage with audiences,
practice their craft, and 
hone their skills~\cite{Hamilton:2014:STF:2611105.2557048,Zhang:2015:CIL:2736084.2736091}.

@@

\begin{tabular}{p{2cm}|p{13cm}}
  \textbf{Term} & \textbf{Plan} \\
\hline
Q1  & Identify potential participants and begin recruiting participants;
      begin preliminary interviews and fieldwork.
      Research specifically focusing on performers' \textit{relationships with audiences}
      and noting areas of frustration for performers and intervention opportunities \\
\hline
Q2  & Qualitative fieldwork toward understanding performers' \textit{relationships with other performers},
      with some attention toward the potential for performer affiliations \\
\hline
Q3  & Fieldwork looking at performers' \textit{relationships with their respective platforms}
      (for example: YouTube, Twitch) \\
\hline
Q4  & Exploring and iterating on \textit{design interventions} with YouTubers and streamers
      to advance values discussed earlier
      (audience engagement, online performer affiliation, etc\dots)  \\
\end{tabular}

\topic{Our interview process will }
We will use semi--structured interviews
to remain open to participants guiding our research agenda toward
whatever they consider to be compelling topics.
With that being said

@@

% \pagebreak
% \renewcommand\bibname{{\small References}}
\setlength\bibitemsep{0pt}

\renewcommand*{\bibfont}{\tiny}

\printbibliography{}
\end{document}

>>>>

% \AtBeginBibliography{\small}
\thispagestyle{empty}

@@

% \def\maketitle{%
% \par{{\scshape \LARGE \textbf{\@title}}%
% \par{\@author}
% \par{DRAFT \DTMcurrenttime~\today}%
% \par}}
% \smallskip \hrule \smallskip }
\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  {\scshape \Large \textbf{\@title}}

  \@author
\end{flushleft}\egroup
}
\makeatother
\definecolor{PineGreen}{HTML}{008800}
\definecolor{Red}{HTML}{FF0000}
\definecolor{Blue}{HTML}{0000FF}
\definecolor{Black}{HTML}{000000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{Red}[al2: #1]}}

\title{An Ethnography of Online Performance Artists}
\author{Ali Alkhatib \& Jeffrey Nagy
--- DRAFT \DTMcurrenttime~\today}
\date{\today}
\urlstyle{same}
\hypersetup{
  colorlinks,
  citecolor=Black,
  urlcolor=Blue}

\definecolor{Blue}{HTML}{0000FF}
\newcommand{\topic}[1]{{\color{Blue}#1}}
% \renewcommand{\topic}[1]{{#1}}
\definecolor{Gray}{HTML}{A0A0A0}
\newcommand{\ugh}[1]{{\color{Gray}#1}}
\newenvironment{blah}{\par\color{Gray}\itshape}{\par}

\renewenvironment{abstract}{%
\hfill\begin{minipage}{0.95\textwidth}
% \rule{\textwidth}{1pt}
\itshape
}
{
% \noindent\rule{\textwidth}{1pt}
\bigskip
\end{minipage}}

\begin{document}
  \maketitle
  \begin{abstract}
  Online video sharing and streaming platforms have flourished into a bustling industry in the past decade.
  % to support an emerging community of unconventional entertainers.
  The artists that have emerged on these platforms since then have
  explored boundaries and experimented with styles and formats,
  influencing both audiences' expectations of performers and of the performances themselves.
  But these shifts have come with turmoil among this new group of artists,
  calling for better understanding of the culture and position of this new, growing group.
  We propose to conduct ethnographic fieldwork in this domain,
  initially informed by a historical framing, but
  ultimately studying how digitally mediated publics such as these affect
  the politics of this group of performers.
  \end{abstract}

% \section*{Situation}
\topic{Video sharing sites like YouTube and Twitch
have captured the attention of audiences of billions of people around the world
in the span of little more than a decade.} % taken on characteristics of
% So widely used are these platforms
% that it would be fair to call them ``publics'' in the Deweyan sense~\cite{dewey2012public,disalvo2009design};
content producers
--- ``YouTubers'' and ``streamers'' ---
have begun to make their livings on these sites.
Indeed, these performers have come to rely on
the technical infrastructure these platforms provide as well as
the access to audiences that these platforms provide as well.
In doing so, these sites have in a real sense democratized media and entertainment industries by
making the avenues to large audiences substantially more accessible.
And thus, in these transformations into publics, what started as
a recreational hobby
has become a bustling hub for professional artists to
engage with audiences,
practice their craft, and 
hone their skills~\cite{Hamilton:2014:STF:2611105.2557048,Zhang:2015:CIL:2736084.2736091}.

@@

\begin{tabular}{p{2cm}|p{13cm}}
  \textbf{Term} & \textbf{Plan} \\
\hline
Q1  & Identify potential participants and begin recruiting participants;
      begin interviews and fieldwork.
      Research specifically focusing on performers' \textit{relationships with audiences}
      and noting areas of frustration for performers and intervention opportunities \\
\hline
Q2  & Qualitative fieldwork toward understanding performers' \textit{relationships with other performers},
      with some attention toward the potential for performer affiliations \\
\hline
Q3  & Fieldwork looking at performers' \textit{relationships with their respective platforms}
      (for example: YouTube, Twitch) \\
\hline
Q4  & Exploring and iterating on \textit{design interventions} with YouTubers and streamers
      to advance values discussed earlier
      (audience engagement, online performer affiliation, etc\dots)  \\
\end{tabular}

\topic{We'll recruit between 10 and 30 YouTube and Twitch content producers whose work is primarily content creation on their respective sites
--- in other words, people who have gone ``full time''.}
Our initial interviews will be semi--structured in nature, as we'll want to be open to the possibility that 
% We will use semi--structured interviews
% to remain open to participants guiding our research agenda toward
% whatever they consider to be compelling topics.

@@

% \pagebreak
% \renewcommand\bibname{{\small References}}
% \setlength\bibitemsep{0pt}

% \renewcommand*{\bibfont}{\tiny}
\pagebreak
\printbibliography{}
\end{document}
